---
title       : Some Metric System Transformations 
subtitle    : Basic Metric Systems
author      : Maria Alexandridou
job         : Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : solarized_light      # 
widgets     : [mathjax,shiny,interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---
## Introduction
This is a presentation of the Shiny Application "My Application"
This Shiny Application utilizes mathematics formulas between
different values to calculate the difference in value between 

1. Celsius and Fahrenheit
2. Kilometers and Miles
3. Centimeters and Inches
4. Meters and Feet
5. Kilograms and Pounds

It is easy to use and does not require any special knowledge.

--- .class #id 
## Formulas:

1. Celsius and Fahrenheit : $$\frac{9C}{5}+32=F$$
2. Kilometers and Miles : $$Mi=Km*0.62137$$
3. Centimeters and Inches : $$Ft=Cm*2.54$$
4. Meters and Feet : $$Ft=M*3.2808$$
5. Kilograms and Pounds $$Lb=Kg*2.2046$$

---
## How it works

Here is a part of the code of the Application
```{r,echo=TRUE,results='hide',warning=FALSE}
library(shiny)
shinyUI(
  mainPanel(
      numericInput('C','Celsius to Fahrenheit',0,min=-273.15,max=200000000 ,step=0.05),
      submitButton('Submit'),
      h4("It has as a result: "),
      verbatimTextOutput("oC")
      )
)
```
and it returns after having computed from behind the scenes the calculation 

result1<-function(C) C*(9/5)+32

---$interactive
## An Example
```{r opts.label='shiny',echo=FALSE, }
shinyUI(
  mainPanel(
    numericInput('C','Celsius to Fahrenheit',0,min=-273.15,max=200000000 ,step=0.05),
    submitButton('Submit'),
    h4("It has as a result: "),
    verbatimTextOutput("oC")
  )
)
```